Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-22 ms.tex
comparison ifurge

\section{Introduction} \label{sec:intro}
It is a truism to say that planets are round.  The. And yet planets' roundness gives rise to a host of complications:  atmospheric circulation, variable , gradients in chemistry, cloud formation and evaporation, and time-dependent phenomena (weather).

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Planets}
cite Tremblin et al. 2017 ? (https://arxiv.org/pdf/1710.02640.pdf)

>>>>

\section{Introduction} \label{sec:intro}
The planets and moons of the Solar System possess a rich variety of -- weather, temperature var

It is a truism to say that planets are round.  The. And yet planets' roundness gives rise to a host of complications:  atmospheric circulation, variable , gradients in chemistry, cloud formation and evaporation, and time-dependent phenomena (weather).

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Planets}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, it is heated asymmetrically, its rotation rate is FIXME faster, and its surface gravity is lower.   To assess the effects of these comparative study with other objects of similar temperature, including field brown dwarfs and young directly imaged companions.

Sample of directly imaged planets

cite Tremblin et al. 2017 ? (https://arxiv.org/pdf/1710.02640.pdf)
